Assessment of zonally symmetric and asymmetric components of the Southern Annular Mode using a novel approach

### 2021-05-13 analysis/paper/asymsam.Rmd
Aclara "positive values" en la regersión

Figure\ \@ref(fig:global-pp) shows regression of the SAM indices with precipitation for the Southern Hemisphere. 
The precipitation signal associated with SAM shows generally decreased precipitation at around 45ºS, somewhat increase precipitation around 30ªS (Fig.\ \@ref(fig:global-pp)a) and increased precipitation over Antarctica, a pattern known from other studies [e.g. @hendon2014].
This pattern is mostly unchanged between seasons albeit from varying in intensity. 
Panels b and c in Figure\ \@ref(fig:global-pp) shows that the A\nobreakdash-SAM signal is only in the tropics and mid-latitudes, while the S\nobreakdash-SAM signal is strong in the higher latitudes. 
In particular S\nobreakdash-SAM is associated with the increased precipitation over Antarctica and decrease precipitation around the Southern Ocean.

>>>>

Figure\ \@ref(fig:global-pp) shows regression of the SAM indices with precipitation for the Southern Hemisphere. 
The precipitation signal associated with SAM shows generally decreased precipitation at around 45ºS, somewhat increase precipitation around 30ªS (Fig.\ \@ref(fig:global-pp)a) and increased precipitation over Antarctica, a pattern known from other studies [e.g. @hendon2014].
This pattern is mostly unchanged between seasons albeit from varying in intensity. 
Panels b and c in Figure\ \@ref(fig:global-pp) shows that the A\nobreakdash-SAM signal is only in the tropics and mid-latitudes, while the S\nobreakdash-SAM signal is strong in the higher latitudes. 
In particular positive values of S\nobreakdash-SAM is associated with the increased precipitation over Antarctica and decrease precipitation around the Southern Ocean.
